\documentclass{article}   
\usepackage{geometry}                	
\geometry{letterpaper} 
\usepackage{graphicx}				
\usepackage{float}
\usepackage{amssymb}
\usepackage{color}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{tabularx}
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=black,
    urlcolor=black
}

\usepackage[normalem]{ulem}
\definecolor{RevisionColour}{rgb}{0.0, 0.6, 0.3}
\newcommand{\rev}[1]{\textcolor{RevisionColour}{#1}}
\title{Problem Statement
}
\author{Liu, Ruoyuan\\
		400033145
		\and
		Chen, Zihao\\
		001405956
		\and
		Kanwal, Gundeep\\
		400015267}
\date{\sout{September, 2017}\rev{December 6, 2017}}
\begin{document}

\maketitle

\newpage
\begin{table}[hp]
	\caption{Revision History} \label{TblRevisionHistory}
	\begin{tabularx}{\textwidth}{llX}
		\toprule
		\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
		\midrule
		09/27/2016 & Ruoyuan, Zihao, Gundeep & Created and finished Development Rev.0\\
		\rev{12/04/2017} & \rev{Ruoyuan} & \rev{Revision 1 Update}\\
		\bottomrule
	\end{tabularx}
\end{table}




\section{What problem are you trying to solve?}

\newcommand*\apos{\textsc{\char13}}
The problem we are trying to solve is the lack of accessibility to fun, simple games which anyone can play. There are many games that are either too complicated for many to enjoy, or games that are just unreachable such as games which require an internet connection \rev{or specific devices and platform}, and with some people, there are cases where some people are just not physically able to entertain themselves through playing many of the digital games out there. We want to make gaming more accessible to as much people as we can in order to provide a way for more people to entertain themselves.

\section{Why is this an important problem?}

There are many games that do not fit all types of audience, they could either be too violent for the young or contain explicit content and they end up limiting the amount of people who would enjoy playing it.  As people are spending more and more time on cell phone entertainment,  it is important to develop a fun, simple game fit all types of audiences.\newline\newline
A lot of existing game sometimes are overly complicated.  It will drain your battery much faster than a simple game as the game have too many modules.  Some games are too difficult in terms of the skill required to play the,, for example, NBA 2K on mobile devices has a lot of buttons to perform different actions.  It becomes especially difficult to play for users with smaller cell phone screens.\newline\newline
Doodle Jump is a game that take little time to develop skill but you \sout{won’t}\rev{will not} get tired with it soon by keep challenging yourself for higher score.\newline\newline
The original doodle jump is a great game but missing a vital element.  In our improved version, we will create a theme in the game that every element will perform in conformity so the users will better immerse themselves than the previous version.  


\section{What is the context of the problem you are solving?}
People who are involving in this project are gamers as users and the N.L.E team as developers.The game genre, infinite jump, \sout{itself} has a quite long history with an acceptance of \sout{wide range of ages} \rev{wide age range} of people and plenty of addicting and intense gameplay. Recreating doodle jump in java can help our user get a easier way to access the game, because java as an environment for program is widely used in many devices. The N.L.E team, as both developer and client, will keep maintaining the game, push\rev{ing} bug fixes to the game after the game finishes, and provid\rev{ing} our users entertainment as much as possible.




\end{document}  

